% table-timeline-2008.tex
% Adjusted widths: total ~15.5 cm to fit exactly inside 1in margins (single-column A4/letter)

\vspace{1em}

\begin{longtable}{
  >{\raggedright\arraybackslash}p{3.0cm}
  >{\raggedright\arraybackslash}p{3.3cm}
  >{\raggedright\arraybackslash}p{9.2cm}
}
\caption{Clinical Timeline of Key Events and Interventions (2008), Reconstructed from Medical Records}
\label{tab:clinical-timeline-2008} \\
\toprule
\textbf{Date} & \textbf{Location} & \textbf{Comments} \\
\midrule
\endfirsthead

\toprule
\textbf{Date} & \textbf{Location} & \textbf{Comments} \\
\midrule
\endhead

\endfoot

8th Feb & GP Surgery
& Tired all the time – denies symptoms of depression, comes over quite anxious, discussed options, check FBC and glucose. \\
\midrule
19th Feb & GP Surgery
& Laboratory investigations otherwise normal, aside from mild isolated unconjugated hyperbilirubinaemia (total bilirubin 37 $\mu$mol/L) and borderline hypokalaemia (3.5 mmol/L). Thyroid function test unknown. \\
\midrule
16th Jul & GP Surgery
& Two weeks off work for depression. Rebound mood swings, low mood, personal problems at home, living with father, PHQ-9 = 19. Plan: start sertraline, review in 4 weeks. \\
\midrule
31st Jul & GP Surgery
& Depressed – much better, fit to return to work, aim to treat for 4 months. \\
\midrule
21st Nov & GP Surgery
& Depressed mood again. Sleep poor. Studying and working. Will try different antidepressant. Plans to move back home with father (feels moving out had bad effect). Rx: citalopram 10 mg daily. See in 1 week. \\
\midrule
15th Dec & GP Surgery
& History: numbness of right side of body, had a “collapse” a few days ago at work and was sent home. Not taking SSRIs (only took a few days’ worth). Feeling tired all the time. \\
& & Examination: normal plantar, knee, thigh adductor and biceps reflexes (all brisk), normal soft touch sensation on both feet (symmetrical). \\
& & Diagnosis: ?schizoaffective personality ?MS. Plan: check bloods including fasting glucose, refer neurology. \\
\midrule
18th Dec & GP Surgery
& Full blood count, renal function, electrolytes, serum calcium (corrected for albumin), bone profile, liver function tests, and thyroid function within normal limits, except for mild isolated unconjugated hyperbilirubinaemia (total bilirubin 37 $\mu$mol/L) and borderline low potassium (3.5 mmol/L). \\
\midrule
21st Dec & Ambulance Service
& Patient fell in street, struck head, was conscious throughout, vital signs normal. Lives alone but will stay with parents temporarily. Advised to call emergency services if any further collapse or loss of consciousness occurs. Refused conveyance. \\
\midrule
23rd Dec & GP Surgery
& History: collapse (seems to have occurred more than once ?seizure – no witness), bedwetting and frequency of urination, odd gait, sleeping a lot, dark urine. \\
& & Examination: odd gait noted, slightly odd affect, fundi normal. \\
& & Plan: reassess, ?early MS – consider referral. Odd social history – used to live with father but now rents; has been staying with mother recently who accompanied him today. \\
\midrule
27th–30th Dec & A\&E $\to$ Royal Free Hospital
& A\&E admission for falls. CT head initially planned as outpatient, but performed as inpatient following father’s intervention. Hydrocephalus diagnosed. Ventriculoperitoneal shunt inserted 30th Dec 2008. \\
\end{longtable}